---
title: "HW2"
author: "Gregorio"
date: "2022-09-01"
output: word_document
---

### 1.) Create a vector x. x contains a sequence of integers from 11 to 16.
```{r}
x <- c(11:16)
```
### 2.) Name the elements of x using words: eleven, twelve, thirteen, fourteen, fifteen and sixteen.
```{r}
names(x) <- c("eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen")
x
```
### 3.) Index the element "twelve - 12" by its name.
```{r}
x["twelve"]
```
### 4.) Index the 3rd and 4th elements in the vector.
```{r}
x[3:4]
```

### 5.) Remove the names in the x vector.
```{r}
names(x) <- NULL
x
```

### 6.) Use filtering to subset values that has a square value larger than or equal to 144. (Hint: use ">=")
```{r}
x[x^2 >= 144]
```
### 7.) Coerce the vector x into a matrix x of 3 rows and 2 columns.
```{r}
dim(x) <- c(3,2)
x
```

### 8.) Transpose the matrix and save it into object y
```{r}
y <- t(x)
y
```
### 9.) Calculate the mean of each row for x using the apply() function.
```{r}
apply(x, 1, mean)
```

